paper_replication

### 2021-12-13 paper_replication.Rmd
Update paper_replication.Rmd

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#load in data
providers <- read.csv("provider_list_geo.csv")
countycentroids <- read.csv("county_pop_centroids.csv")
countydem <- read.csv("county_demographics.csv")
abortions <- read.csv("cleanedabortiondata.csv")
restrictions <- read.csv("state_restrictions2010.csv")
```

@@

countypres <- read.csv("countypres.csv")
countypresdem2008 <- countypres %>% filter(party == "DEMOCRAT" & year == 2008)
countypresdem2008$county_name <- str_to_title(countypresdem2008$county_name)
countypresdem2008$county_name[!(countypresdem2008$county_name %in% countydem$county)]

@@

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#load in data
providers <- read.csv("provider_list_geo.csv")
countycentroids <- read.csv("county_pop_centroids.csv")
countydem <- read.csv("county_demographics.csv")
abortions <- read.csv("cleanedabortiondata.csv")
restrictions <- read.csv("state_restrictions2010.csv")
countypres <- read.csv("countypres.csv")
```

@@

```{r}
## calculate percent democratic votes
countypresdem2008 <- countypres %>% filter(party == "DEMOCRAT" & year == 2008)
countypresdem2008$county_name <- str_to_title(countypresdem2008$county_name)
countypresdem2008$county_name[!(countypresdem2008$county_name %in% countydem$county)]

@@

```{r}
#make new variable for high vs. low restrictions
restrictions <- restrictions %>% mutate(totalrestrict = parental_involvement + two_trips + trap + unconstitutional_ban, 
                                        highorlow = case_when(totalrestrict >= 3 ~ "high", 
                                                              totalrestrict < 3 ~ "low"))
```

```{r}
#make propensity scores
